A secondary screen architecture to accurately capture viewers' interactions in an iTV environment

### 2014-05-17 src/paper.tex
Revision finished

The architecture to accurately capture viewers interactions is shown in \figurename~\ref{fig_architecture}. This architecture consists of secondary screen devices (which might be implemented in personal devices such as smartphones and tablets) an iTV device, and the CP infrastructure (which includes an application hosting infrastructure). The green arrows represent the data flowing from the viewer to the CP infrastructure, while blue arrows denote the flow from CP infrastructure to the viewers. The black arrows represent the data flow inside the CP infrastructure.

@@

A presence service detects nearby secondary screen devices that have the services necessary for establishing a communication with iTV device. Once the secondary screen device is linked up with the iTV device in the same environment, they are synchronized in order to update contextual data about viewer profile and amount of people using a secondary device in the room. This contextual information can be used to learn how a viewer behave toward other viewers. For example, a viewer behaves in a particular way while watching TV alone and the same viewer can behave in a different way while watching in group.

Viewers can use their secondary screen device to interact with TV by evaluating, commenting, sharing or even recommending TV content to other viewers. These interactions and the contextual information are represented by the audience data that is then sent to CP infrastructure through Internet. Then, a Data Writer service stores the audience data related to each particular viewer and the iTV device.

@@

This is paper presents an architecture to accurately capture audience data in interactive TV by using secondary screen devices. The implementation of this architecture is a work in progress and its main goal is to capture viewers' interactions and contextual information to use in applications for interactive TV environments.

@@

The use of personal devices as secondary screens arises as a new trend in TV environments. The architecture described in this paper take advantage of the ubiquity and interactive capabilities of secondary screen devices to identify viewers and provide feedback for CPs through viewers' interactions and contextual information.

>>>>

The architecture to accurately capture viewers interactions is shown in \figurename~\ref{fig_architecture}. This architecture consists of secondary screen devices (which might be implemented in personal devices such as smartphones and tablets) an iTV device, and the CP infrastructure (which includes an application hosting infrastructure). The dashed green arrows represent the data flowing from the viewer to the CP infrastructure, while dotted blue arrows denote the flow from CP infrastructure to the viewers. The continuous black arrows represent the data flow inside the CP infrastructure.

@@

A presence service detects physically nearby secondary screen devices that have the services necessary for establishing a communication with iTV device. Modern commercial operating systems for personal devices enable service discovery by using peer-to-peer or WiFi communication. This feature is particularly appropriate for the TV environment, once the secondary screen device must be wirelessly linked up with the iTV device. The devices are synchronized in order to update contextual data about viewer profile and amount of people using a secondary device in the room. This contextual data can be used to learn how a viewer behave toward other viewers. For example, a viewer behaves in a particular way while watching TV alone and the same viewer can behave in a different way while watching in group.

Viewers can use their secondary screen device to interact with TV by evaluating, commenting, sharing or even recommending TV content to other viewers. The data related to those actions are naturally provided by the viewers as part of the interaction when using interactive applications (developed by the CP) installed in their secondary screen devices. The interactions and the contextual data are represented by the audience data, which is sent to CP infrastructure through Internet. Then, a Data Writer service stores the audience data related to each particular viewer and the iTV device.

@@

The use of personal devices as secondary screens arises as a new trend in TV environments. This is paper presents an architecture to accurately capture audience data by using secondary screen devices and iTV devices. The implementation of this architecture is a work in progress, and take advantage of the ubiquity and interactive capabilities of secondary screen devices to identify viewers and provide feedback for CPs through viewers' interactions and contextual information.

@@

The architecture described in this paper is also technically feasible to implement in Digital TV (DTV) systems and can be particularly interesting for CPs in DTV standards like the Brazilian (ISDB-TB) and the Japanese(ISDB-T). These standards support the use of mobile devices as part of the system. So, since the mobile devices support the implementation of the DTV middleware, a cooperative exhibition of the DTV application can be managed with the iTV device, thus enabling the capture of viewers' interactions and contextual data.
